---
title: "2023 RAFWE WFGRS Workshop"
author: "Christopher Cousins"
date: "2023-03-30"
output: html_document
---

let's set the seed to be able to reproduce the data
```{r}
set.seed(66)
```

Now let's generate some data!
Here I'll create a dataset, let's say they're DBH measurements (look I'm being nice to the forestry folks)
I'll call the dataset DBH, and have it pull 16 values from a normal distribution, with a mean of 6 and sd of 2
```{r}
DBH <- rnorm(n = 16, mean = 6, sd = 2)
```

Ok, now we have 16 DBH measurements!

Now, let's make another dataset.
This one will be abundances for clouded salamanders found in each tree (now it's the wildlife people's turn to be happy)
I'll call the dataset Sallys, and have it pull 16 values from a normal distribution, with a mean of 20 and sd of 6
```{r}
Sallys <- rnorm(n = 16, mean = 20, sd = 6)
```

Great! Now this isn't a lot of code, but often when we're preparing data for analysis it's A TON OF CODE!

It can be annoying to have to run through code a lot, 
so let's just export these datasets to our github to use in another script.
First we'll set the working directory to the github folder (This is where you'll have to change this to match your PC)
Then we'll export this to the github folder
```{r}
setwd("C:/PhD/Git/RAFWE.WFGRS.2023")
save(DBH, Sallys, file = "./04.RCodingandFork/datasetcreation/sallysonwood.RData")
```

Ok we're done here, let's move on. But first, let's clear our environment
```{r}
rm(list=ls())
```

Ok close this and let's open the next script.
