---
title: "2023 RAFWE WFGRS Workshop"
author: "Christopher Cousins"
date: "2023-03-30"
output: html_document
---

let's get ggplot
```{r}
library(ggplot2)
```

ok, let's pull in that model, and the datasets
first we'll set the working drive, then load from there
```{r}
setwd("C:/PhD/Git/RAFWE.WFGRS.2023")
load("./compartmentalizedRcoding/simulatedmodels/model.RData")
load("./compartmentalizedRcoding/datasetcreation/sallysonwood.RData")
```
Ok cool, look at that, our model and datasets is ready to go

ok cool, now let's make a scatter plot with a regression line and confidence intervals
```{r}
sallysandwoodplot <- ggplot(model, aes(DBH, Sallys)) +
  geom_point() +
  stat_smooth(method = lm)

sallysandwoodplot
```

so, let's save this plot as a png
```{r}
png(file = "./simulatedgraphs/sallygraph.png")

ggplot(model, aes(DBH, Sallys)) +
  geom_point() +
  stat_smooth(method = lm)

dev.off()
```

Ok we're done here, let's move on. But first, let's clear our environment
```{r}
rm(list=ls())
```

Ok close this and let's open the next and final script, to run some analysis