---
title: "2023 RAFWE WFGRS Workshop"
author: "Christopher Cousins"
date: "2023-03-30"
output: html_document
---


ok, let's pull in that model, and the datasets
first we'll set the working drive, then load from there
```{r}
setwd("C:/PhD/Git/RAFWE.WFGRS.2023")
load("./compartmentalizedRcoding/simulatedmodels/model.RData")
load("./compartmentalizedRcoding/datasetcreation/sallysonwood.RData")
```
Ok cool, look at that, our model and datasets is ready to go

alright, for the final example, let's do some analysis
```{r}
summary(model)
```
ok, looks like there is no statistical significance between the width of the wood and the amount of sallys on it
hit that little collapse arrow in the upper right hand corner to minimize the table, and let's move on

ok your pi doesn't believe you, they were so confident in their predictions, so they're gonna need some cold hard data to convince them otherwise. let's get some together.

let's take the confidence intervals and save them
```{r}
sadness <- confint(model)
setwd("C:/PhD/Git/RAFWE.WFGRS.2023")
save(sadness, file = "./compartmentalizedRcoding/simulatedanalysis/sadness.RData")
```

your pi should be able to open that, but whoops, turns out they don't know how to use R. no problem, let's make a table
```{r}
write.table(sadness, file="./simulatedanalysis/itoldyou.txt", sep = ",", quote = FALSE)
```
Now you have a text file with the confidence intervals, gg wp

Ok we're done here, let's move on. But first, let's clear our environment
```{r}
rm(list=ls())
```

Yo it all worked, look at us go. 
Who woulda thought?
Not me. :)
